A holomorphic approach to membranes and fivebranes

### 2022-06-15 fivebranes/fact.tex

\begin{rmk}
The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
From the data of a factorization algebra, one can recover local operators by the following formal construction.

Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.

Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures \brian{difference between limit and homotopy limit}
\end{rmk}

At the quantum level this Chevellay--Eilenberg complex is deformed.
The BV formalism ...
Even in perturbation theory the full quantum behavior of the holomorphical-topological eleven-dimensional theory is an open question. 
We leave the problem to characterize the quantization to future work.

\subsection{The factorization algebra associated to twisted supergravity}

In this section we consider the classical factorization algebra of observables of our prototype for the holomorphic twist of eleven-dimensional supergravity.

\parsec[s:sugraobs]

As above, let $X$ be a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
In the first section we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential.

The $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset X \times S$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]
We will denote the entire classical factorization algebra on $X \times S$ of classical observables by~$\clie^\bu(\cL_{sugra})$.

@@

\parsec[s:restricted]

With an eye towards holography for fivebranes we fix a complex three-fold $Z$ where the fivebranes will be supported and consider the eleven-dimensional theory on $\R \times X_Z$ where $X_Z$ is the Calabi--Yau fivefold
\[
X_Z = \text{Tot}(K_Z^{1/2} \otimes \C^2),
\]
the total space of the rank two bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
Here the holomorphic volume form
One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over $Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
Let 
\[
\pi \colon \R \times X_Z \to Z 
\]
be the map which projects out the real factor followed by the projection to the base of the total space of the complex rank two bundle $p \colon X_Z \to Z$.

@@

\parsec[s:gradingfivebrane]

@@

The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
The argument is nearly identical so we omit the details.

\end{proof}

For each $n \in \ZZ$ and open set $U \subset Z$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.

\begin{prop}
For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
\[
\Omega^{0,\bu}(U, \cV^{(n)})
\]
for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$.
For each $n$, the differential is of the form $\dbar + Q^{hol}$.
In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
\end{prop}

We explicitly describe the first homogenous weights of $\Bar{\pi}_* \cL_{sugra}$.

@@

As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
We will show that 
\[
\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
\]
whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight zero summand $\cV^{(0)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{1/2}_Z$ we see that these are local sections of $K^{1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

@@

Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is quasi-isomorphic to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
In other words, the weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

As a holomorphic vector bundle, we will see that $\cV^{(0)}$ is 
\[
\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.

@@

The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV^{(0)})$. 
The differential is simply $\dbar$. 
The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
\begin{itemize}
\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
\item Finally, and most interestingly, there is a bracket of the form
\[
\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
\]
given in coordinates by
\[
[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right).
\]
\end{itemize}

@@

Now, since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
\[
U\subset \C^3 \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
\]
has the structure of a factorization algebra on $\C^3$ which we denote by $\Bar{\pi}_* \Obs_{sugra}$.

\begin{prop}
Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
\begin{itemize}
\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
\[
\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
\]
which is dense at the level of cohomology. 
\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
\beqn\label{eqn:decomp3}
\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
\eeqn
\item[(3)]
In weight zero, there is an equivalence of local Lie algebras on $Z$ 
\[
\cV_0 \simeq \cE(3|6)|Z 
\]
where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
\end{itemize}
\end{prop}

@@

\subsection{Koszul duality for factorization algebras: an ansatz}

>>>>

\begin{rmk}
The notion of a factorization algebra captures both the local and non-local operators in a quantum field theory. 
Indeed, from the data of a factorization algebra, one can recover local operators by the following formal construction. 
Let $\Obs$ be a factorization algebra on a smooth manifold $M$.
The classical \defterm{point observables} at $p \in M$ is the limit $\Obs(p) = \lim_{U \ni p} \Obs(U)$ where the limit runs over open sets $U \subset M$ containing $p$.
Generally this limit is difficult to compute, but for certain theories it is possible to give a concise expression which captures the essential features of the theory.
For example, in a holomorphic theory, the algebra of local operators is equivalent to the algebra generated by holomorphic derivatives of fields evaluated at a point \cite{CG2}.
\end{rmk}

At the quantum level this Chevellay--Eilenberg complex is deformed.
The BV formalism ...
Even in perturbation theory the full quantum behavior of the holomorphical-topological eleven-dimensional theory is an open question. 
We leave the problem to characterize the quantization to future work. 
\brian{add discussion}

In this section we will consider the classical factorization algebra of observables of our prototype for the minimal twist of eleven-dimensional supergravity given in \S \ref{s:twisted} which is defined on $S \times X$ where $X$ is a Calabi--Yau fivefold and $S$ a real oriented one-manifold. 
%In the \S \ref{s:twisted} we recalled a proposal for the description of the minimal twist of eleven-dimensional supergravity on $S \times X$. 
The primary object we used to describe the solutions of the equations of motion was the $\Z/2$ graded local $L_\infty$ algebra $\cL_{sugra}$, see \S \ref{s:Lsugra}. 
%As a graded vector space, observables on an open set $U \subset X \times S$ are thus $\cO(\cL_{sugra}(U)) = \Sym (\Pi \cL_{sugra})^\vee$.
%The differential is encoded by the $L_\infty$ structure which is exactly the Chevalley--Eilenberg differential.

In terms of this local $L_\infty$ algebra, the $\Z/2$ graded commutative dg algebra of classical observables supported on an open set $U \subset S \times X$ is 
\[
\clie^\bu\left(\cL_{sugra}(U)\right) .
\]
We will denote the entire classical factorization algebra on $S \times X$ of classical observables by~$\Obs_{sugra}$.

@@

\subsection{The fivebrane decomposition}\label{s:resm5}

With an eye towards holography for fivebranes we fix a complex three-fold $Z$ where the fivebranes will be supported and consider the eleven-dimensional theory on $\R \times X_Z$ where $X_Z$ is the Calabi--Yau fivefold
\[
X_Z = \text{Tot}(K_Z^{1/2} \otimes \C^2),
\]
the total space of the rank two holomorphic vector bundle $K_Z^{1/2} \otimes \C^2$ over $Z$. 
%In the remainder of this section we denote by $V \to Z$ this rank two holomorphic vector bundle. 
One can also think about $\R \times X_Z$ as the total space of the {\em real} rank five bundle over $Z$; although this description obfuscates the geometric structure used to define the eleven-dimensional theory.
Let 
\[
\pi \colon \R \times X_Z \to Z 
\]
be the map which projects out the real factor followed by the projection to the base of the total space of the complex rank two bundle $p \colon X_Z \to Z$.

@@

@@

The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
The argument is nearly identical so we omit the details. 
\end{proof}

For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.

\begin{lem}
\label{lem:technical}
For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
\[
\Omega^{0,\bu}(U, \cV_{fivebrane}^{(n)})
\]
for some finite rank super holomorphic vector bundle $\cV_{fivebrane}^{(n)}$ on $Z$.
For each $n$, the differential is of the form $\dbar + Q^{hol}$.
In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $Z$. 
\end{lem}

\begin{proof}
In \S \ref{s:Lsugra} we introduced a holomorphic vector bundle $L_X$ defined on any Calabi--Yau five-fold $X$ whose sheaf of holomorphic sections was equipped with a $\Z/2$ graded $L_\infty$ structure. 
Here, we consider the Calabi--Yau fivefold $X = X_Z$ as defined above.
For any open subset $U \subset Z$ of the threefold the value of $\cL_{sugra}(\pi^{-1}U)$ as a sheaf of super vector spaces is 
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}(p^{-1} U, L_{X_Z}),
\]
where $p \colon X_Z \to Z$ is the rank two bundle over $Z$. 
The one-ary structure map, or differential, is of the form $\d_{dR} + \dbar + Q^{hol}$ where $Q^{hol}$ is some odd holomorphic differential operator acting on sections of $L_{X_Z}$.

Since the de Rham complex of $\R$ is contractible we have a quasi-isomorphism of $L_\infty$ algebras
\[
\cL_{sugra}(\pi^{-1}U) \simeq \Omega^{0,\bu}(p^{-1} U, L_{X_Z})
\]
for every $U \subset Z$. 
Without loss of generality, we can assume that $U$ is a coordinate chart for the vector bundle $X_Z$ so that $X_Z|_U \cong U \times \C^2$ and where the bundle $L_{X_Z}$ splits as 
\[
L_{X_Z}|_{\pi^{-1} U} \cong L' \boxtimes L'' 
\]
where $L'$ is a holomorphic super vector bundle on $U$ and $L''$ is.a holomorphic vector on the fiber $\C^2$.
Then, we can further identify this with a Dolbeault complex of the form
\[
\Omega^{0,\bu} \left(U, L' \otimes \Omega^{0,\bu}(\C^2, L'') \right) . 
\]
By the Dolbeault Poincar\'e lemma applied to the holomorphic vector bundle $L''$ over $\C^2$,
\[
\Omega^{0,\bu} \left(U, L' \otimes M\right) 
\]
where we now interpret $L' \otimes M$ as an infinite rank bundle over $U \subset Z$---
the remaining differential is $\dbar_U + Q^{hol}$ where $Q^{hol}$ is a holomorphic differential operator.

With these simplifications, it suffices to show that the weight $n$ eigenspace of $L' \otimes M$ is finite rank over $U$ \brian{almost finished}
%we can fix a quasi-isomorphism $M \simeq \Omega^{0,\bu}(\C^2, L'')$ where $M$ is a 
\end{proof}

We explicitly describe the first few homogenous eigenspaces of $\Bar{\pi}_* \cL_{sugra}$.

@@

As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(-1)})$. 
We will show that 
\[
\cV_{fivebrane}^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
\]
whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight zero summand $\cV_{fivebrane}^{(0)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{1/2}_Z$ we see that these are local sections of $K^{1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

@@

Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

As a holomorphic vector bundle, we will see that $\cV_{fivebrane}^{(0)}$ is 
\[
\cV_{fivebrane}^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.

@@

The $L_\infty$ structure on $\Bar{\pi}_* \cL_{sugra}$ induces the structure of a local $\Z/2$ graded dg Lie algebra on $\Omega^{0,\bu}(Z, \cV_{fivebrane}^{(0)})$. 
The differential is simply $\dbar$. 
The Lie bracket is induced from a Lie algebra structure on holomorphic sections of $\cV_{fivebrane}^{(0)}$ which we can describe as follows:
\begin{itemize}
\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
\item Finally, and most interestingly, there is a bracket of the form
\[
\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
\]
given in coordinates by
\[
[f^a(z) \d w_a , g^a \d w_b] = \left(??, ??\right) 
\]
\brian{finish}
\end{itemize}

@@

Since $\Bar{\pi}_* \cL_{sugra}$ is a pro-vector bundle with a compatible $L_\infty$ structure, the assignment 
\[
U\subset Z \mapsto \clie^\bu\left(\Bar{\pi}_* \cL_{sugra}(U)\right) 
\]
has the structure of a factorization algebra on the three-fold $Z$. 
We denote this factorization algebra by $\Bar{\pi}_* \Obs_{sugra}$.

%\begin{prop}
%Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
%There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
%\begin{itemize}
%\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
%\[
%\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
%\]
%which is dense at the level of cohomology. 
%\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
%\beqn\label{eqn:decomp3}
%\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
%\eeqn
%\item[(3)]
%In weight zero, there is an equivalence of local Lie algebras on $Z$ 
%\[
%\cV_0 \simeq \cE(3|6)|Z 
%\]
%where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
%\end{itemize}
%\end{prop}

@@

\subsection{The membrane decomposition}

We briefly go through an analogous decomposition for membranes. 
For this, we fix a Riemann surface $C$ and consider the eleven-dimensional theory on $\R \times X_C$ where $X_C$ is the Calabi--Yau fivefold
\[
X_C = \text{Tot}(K_C^{1/4} \otimes \C^4),
\]
the total space of the rank four bundle $K_C^{1/4} \otimes \C^2$ over $C$.
Denote by 
\[
\pi \colon V \to \R \times C
\] 
the pullback of this vector bundle along the projection $\R \times C \to C$.
We can equivalently think of the eleven-manifold as the total space of the bundle $V$ over $\R \times C$. 
In this description, the twisted membranes will be supported along the zero section of $V$. 
The factorization algebra $\Obs_{sugra}$ on ${\rm Tot}(V)$ can be pushed forward along $\pi$ to a factorization algebra $\pi_* \Obs_{sugra}$ on $\R \times C$.

As in the fivebrane case, this is not the factorization algebra associated to an ordinary field theory on $\R \times C$.
Nevertheless there is a subfactorization algebra which admits a natural grading so that each filtered component can be understood as such.
This grading is determined by a (different) $\C^\times$ action on the fields of the eleven-dimensional theory on ${\rm Tot}(V) \cong \R \times X_C$ which we now describe.

In a local THF chart $U \subset \R \times C$ we can write a generic field of the eleven-dimensional theory on $\pi^{-1} U$ in coordinates as $f(t;z,w)$ where $(t;z) \in U \subset\R \times C$ is THF coordinate and $w=(w_1,w_2,w_3,w_4)$ is the holomorphic fiber coordinate of the rank four bundle $V$.

With this notation in place, we introduce the following $\C^\times$ action on the fields of the eleven-dimensional theory:
\begin{itemize}
\item On the fields $\mu(t;w,z)$ the action is
\[
\lambda \cdot \mu(t;z,w) = \mu(t; z , \lambda w).
\]
\item On the fields $\nu(t;w,z)$ the action is
\[
\lambda \cdot \nu(t;z,w) = \nu(t;z ,\lambda w).
\]
\item On the fields $\beta(t;w,z)$ the action is
\[
\lambda \cdot \beta(t;z,w) = \lambda^{-1} \beta(t; z, \lambda w).
\]
\item On the fields $\gamma(t;w,z)$ the action is
\[
\lambda \cdot \gamma(t;z,w) = \lambda^{-1} \gamma(t; z ,\lambda w).
\]
\end{itemize}

\begin{prop}
The $L_\infty$ structure on $\pi_* \cL_{sugra}$ is equivariant for this $\C^\times$ action. 
%The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
\end{prop}

As in the case of fivebranes, this proposition allows us to decompose the local Lie algebra $\pi_* \cL_{sugra}$ into eigenspaces. 
Similarly to the proof of Lemma \ref{lem:technical} one can show that the $n$th eigenspace is quasi-isomorphic to a local Lie algebra of the form
\[
\Omega^\bu(\R) \otimes \Omega^{0,\bu}\left(C, \cV_{membrane}^{(n)}\right)
\]
where $\cV^{(n)}_{membrane}$ is a holomorphic super vector bundle on $C$.

We will state explicit descriptions of the first few eigenspaces without details of the proof. 
The first nontrivial eigenspace is, as in the fivebrane case, $n=-1$. 
Here, one can see that 
\[
\cV^{(-1)}_{membrane} \simeq K_{C}^{1/4} \otimes \C^4 \oplus \Pi K^{3/4}_C \otimes \C^4 .
\]
For $n=0$ one has 
\[
\cV^{(0)}_{membrane} \simeq \T_C \oplus \lie{sl}(4) \otimes \cO_C \oplus \Pi \left(K^{-1/2}_C \otimes \wedge^2 \C^4 \oplus K^{-1/2}_C \otimes S^2 \C^4\right) .
\]
\subsection{Koszul duality for factorization algebras: an ansatz}

### 2022-06-15 fivebranes/twisted.tex

In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]
The full space of BV fields of the holomorphic twist is the sections of the $\Z \times \Z/2$ graded sheaf $\cL_{single}[1]$.

@@

The theory in the backreacted geometry will be defineed to be a deformation of the 11d theory placed on the complement of the zero section. The complement of the zero section admits additional structures inherited from the obvious THF structure on $\R \times X$. Note that $\R\oplus V$ has an obvious rank 1 subbundle together with a complex structure on the quotient. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. The fiber spheres have a canonical foliation

>>>>

In the (degenerate) BV formalism, this free theory can be packaged into the data of an abelian $\Z \times \Z/2$ graded local Lie algebra on $Z$ which is of the form 
\[
\cL_{single} = \Omega^{\geq 2, \bu}(Z) \oplus \Pi \Omega^{0,\bu}(Z, K^{1/2}_Z) \otimes \C^2 .
\]

@@

We begin by describing the complement of the zero section
\[
M = \R\oplus V \setminus 0\times Z.
\]

Note that $\R \times X$ is equipped with a natural transverseley-holomorphic foliation - the complexified tangent bundle decomposes as $T_{\R}\oplus T_{Z}\oplus \bar T_{Z}$. Accordingly, we may choose as fiber coordinates $t, w_{1}, w_{2}, \bar w_{1}, \bar w_{2}$ and a fiberwise partially hermitian metric $h$. Explicitly, the corresponding norm is given by
\begin{align*}
 \pi:  \R\times X & \to \R_{+} \\
  (t, w_{i}, \bar{w_{i}}, p)& \mapsto t^{2} + |w_{1}|^{2}+|w_{2}|^{2}
\end{align*}
Letting $p : \R\times X \to Z$, we have an $S^{4}$-bundle $(\pi, p) : \R\times X - Z \to \R_{>0}\times Z$. Let $V_{M}$ denote the vertical tangent bundle to $(\pi, p)$, which we view as a subbundle of the real tangent bundle $T_{M}$. The complexification $V_{M}^{\C}$ inherits some natural subbundles coming from the ambient THF structure. Indeed, letting $\iota : M \to \R\times X$ denote the standard inclusion, we may consider the pair
\[
  V_{M}\cap \iota^{*} T_{\R}, \ \ \ \ \ V\cap \iota^{*} T_{Z}.
\]

The fibers of the composition $V_{M}\to M\to \R_{+}\times Z$ are copies of the tangent bundle of $S^{4}$, and the corresponding fibers of $V_{M}$ are subbundles of $TS^{4}$ that equip the fiber 4-spheres with a generalized Cauchy-Riemann structure. \surya{CITE}

We wish to describe the pushforward $(\pi, p)_{*}\cL_{sugra}$. The underlying sheaf of cochain complexes is given by

\[
\Omega^{\bullet}(\R_{+})\otimes \left ( \begin{tikzcd}
\ul{\rm even} & \ul{\rm odd} \\
\PV^{1,\bu}(Z) \ar[r, "\del_{\Omega}"] & \PV^{0,\bu}(Z)\\
\Omega^{0,\bu}(Z) & \Omega^{1,\bu}(Z) \ar[l, "\del"]
\end{tikzcd}
 \right ) \otimes CR (S^{4}).
\]

Here $CR (S^{4})$ denotes the cohomology of the tangential Cauchy-Riemann complex of $S^{4}$ \surya{CITE}, equipped with the above Cauchy-Riemann structure. Its computation is facilitated by the following lemma:

\begin{lem}
  Let $\R^{d}\times \C^{n}$ be an affine THF manifold, and choose a partial hermitian metric. Let $S^{d+2n-1}$ denote the corresponding unit sphere, equipped with its standard generalized Cauchy-Riemann structure. Then there is a quasi-isomorphism

  \[CR (S^{n+2d-1})\cong \cA^{\bu;\bu}\left ( (\R^{d}\times \C^{n})\setminus 0 \right )\]

  where the right-hand-side denotes the Dolbeault-deRham complex.
\end{lem}

The cohomology of the Dolbeault-deRham complex of $\R\times \C^{2}$ is easy to describe.
